---
title: "Mapping"
author: "Jack Sudds"
date: "06/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse) #install.packages("tidyverse")
library(readxl) #install.packages("readxl")
library(here) #install.packages("here")
library(janitor) #install.packages("janitor")
library(kableExtra) #install.packages("kableExtra")
library(skimr) #install.packages("skimr")
library(dplyr) #install.packages("dplyr")
library(RColorBrewer) #install.packages("RColorBrewer")
library(formattable) #install.packages("formattable")
library(wesanderson)#install.packages("wesanderson")
library(reshape2)
library(ggtext) #install.packages("ggtext")
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggrepel) #install.packages("ggrepel")
```

```{r import}

latlong <- read_excel(here("data", "FelisFelix.xlsx"), sheet = "UK_latlong")

EU <- read_excel(here("data", "FelisFelix.xlsx"), sheet = "EU_latlong")

world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)
```

```{r map making}

ggplot(data = world) +
  geom_sf() +
  theme_minimal() +
  coord_sf(xlim = c(-5.5, 2.50), ylim = c(49.8, 56), expand = FALSE) +
  xlab("Longitude") + ylab("Latitude") +
  geom_point(data = latlong, aes(x = long, y= lat))+
  geom_label_repel(data = latlong, aes(label = Marker, x = long, y = lat, fontface = "bold"),label.size = NA, fill = "#FF0000", color = "black", segment.colour = "#FF0000", max.overlaps  = Inf, min.segment.length = 0)+
  scale_fill_discrete(aesthetics = c("fill", "segment.color"))

ggsave(here("figure", "samples.jpeg"), last_plot(), dpi = 700)

ggplot(data = world) +
  geom_sf() +
  theme_minimal() +
  coord_sf(xlim = c(-12, 25), ylim = c(35, 62.5), expand = FALSE) +
  xlab("Longitude") + ylab("Latitude") +
  geom_point(data = EU, aes(x = long, y= lat))+
  geom_label_repel(data = EU, aes(label = Marker, x = long, y = lat, fontface = "bold"),label.size = NA, fill = "#FF0000", color = "black", segment.colour = "#FF0000", max.overlaps  = Inf, min.segment.length = 0)+
  scale_fill_discrete(aesthetics = c("fill", "segment.color"))

ggsave(here("figure", "EU.jpeg"), last_plot(), dpi = 700)